Hydras \& Co.

### 2022-07-27 doc/ordinal-chapter.tex
Remove the example of termination of list merge (can be solved with omega)
More compatibility 8.15 8.16 + new example on Ackermann function

\subsection{A proof of termination using \texorpdfstring{$\omega^2$}{omega^2}} 
\label{sect:merge-example}

Using the lemma of Sect.~\vref{sect:measure-ON}, we can define easily a total function which merges two lists (example contributed by Pascal Manoury).

%\index{coq}{Commands!Function}

\inputsnippets{ON_Omega2/Merge, ON_Omega2/Mergeb}

>>>>

%%% removed (bad example for omega*omega )

% \subsection{A proof of termination using \texorpdfstring{$\omega^2$}{omega^2}} 
% \label{sect:merge-example}

% Using the lemma of Sect.~\vref{sect:measure-ON}, we can define easily a total function which merges two lists (example contributed by Pascal Manoury).

% %\index{coq}{Commands!Function}

% \vspace{4pt}
% \noindent\emph{From Module~\href{../theories/html/hydras.OrdinalNotations.ON_Omega2.html}{OrdinalNotations.ON\_Omega2}}

% \inputsnippets{ON_Omega2/Merge, ON_Omega2/Mergeb}

\subsubsection{Example: Ackermann function}

\index{maths}{Ackermann function}
\index{coq}{Plug-ins!Equations}

The famous Ackermann function can be defined with the \texttt{Equations} plug-in~\cite{sozeau:hal-01671777}, with a measure towards $\omega^2$.

\vspace{6pt}
\noindent
From~ \href{../theories/html/hydras.OrdinalNotations.ON_Omega2.html}{OrdinalNotations.ON\_Omega2}.

\inputsnippets{ON_Omega2/AckOmega2}
